### 2021-02-09 paper/model/summary.tex
Mention Troeger's research.

Our model also allows the evaluation of different testing strategies by having a detailed
three-step model of test demand, allocation and processing:
First, individuals demand a test because they, e.g., experience symptoms.
Secondly, tests are allocated to individuals while respecting governmental access
restrictions to test.
Thirdly, depending of the capacities of laboratories, tests are processed for some time
until the individual receives her test result.

>>>>

Our model also allows the evaluation of different testing strategies by having a detailed
three-step model of test demand, allocation and processing:
First, individuals demand a test because they, e.g., experience symptoms.
Secondly, tests are allocated to individuals while respecting governmental access
restrictions to tests.
Thirdly, depending of the capacities of laboratories, tests are processed for some time
until the individual receives her test result.
This framework would allow to evaluate the effect of different testing demand behavior
and allocation policies, as are for example discussed by \cite{Troeger2020}.
